\textbf{Computational Fuzzy Extractors}

### 2013-04-05 CompFuzzExt.tex
Switched HILL imp to relaxed HILL

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.  %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the size of a ball in the metric space \lnote{not the most clear sentence}.  
%These results are strongest for high entropy sources.  The results get weaker as we consider sources with lower starting entropy.  If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
We recall a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}, as extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.

\begin{definition}
Let $(X, Z)$ be a pair of random variables.  $X$ has 
\emph{conditional HILL entropy} at least $k$ conditioned on $Z$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(X|Z)\geq k$ if there exists a collection of
distributions $Y_z$ for each $z\in Z$, giving rise to a joint distribution
$(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((X, Z),(Y,Z))\leq \epsilon$.
\end{definition}

\lnote{is there any reason we can't work for the more relaxed notion of HILL, where the condition can be changed, too?}Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches cannot  perform much better than the information-theoretic ones. \lnote{this paragraph needs rephrasing and better gluing with the next one}

%Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
%  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

Suppose we redefine secure sketches using HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$. 
Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches). For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.  In order to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ such that $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $(Y, \sketch(W))$ is computationally indistinguishable from $(W, \sketch(W))$.  Sample a sketch $s\leftarrow \sketch(W)$. We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).  So, by indistinguishability, it must also succeed on $Y$: specifically, $\rec (y',s) = y$ with high probability, for $y\leftarrow Y|s$ and $y'\leftarrow B_t(y)$).
 This means we can construct a large set $C$ from the support of $Y|s$.  $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.

To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
\end{definition}
We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context. \lnote{ do we need this? if distance is exactly $t'$, then the point is different as long as $t'>0$.  So why not just say "exactly $t'$ in the definition?}

@@

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \lnote{is there a source we can reference for the terms average-error and maximal-error?}

 \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We can now formalize the intuition above.  A sketch that retains $\tilde{m}$-bits of HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood \lnote{why $s_{neigh}$ and not $s_{sam}$ as above?} samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$ \lnote{I don't think the asymptotics work here -- we are using concrete parameters, nothing is going to $\infty$, so what does $\Omega$ mean?} .  Then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).  The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$ \lnote{same comment about $\Omega$}, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+t\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\begin{construction}
\label{cons:decoding algorithm} Suppose that for a $(n, m, q, \chi)$ where $m\geq 2n$.  We describe inverter $\mathcal{I}_t$:
\begin{enumerate}
\item Input $\vA , \vect{C} = \vA X + W - W'$
\item Randomly select rows without replacement $i_1,..., i_n\leftarrow [1,m]$.  
\item Restrict $\vA, \vect{C}$ to rows $i_1,...,i_n$, denote this as $A_{i_1,...,i_n}, C_{i_1,...,i_n}$.
\item Compute $X' = \vA^{-1}_{i_1,...,i_n}\vect{C}_{i_1,...,i_n}$.  If $C- AX'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $X'$.
\end{enumerate}
\end{construction}

>>>>

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.  %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch is at most $n - |B_t(\cdot)|$.  For comparison, random linear codes achieve unpredictability $n(1-o(1)) - B_t(\cdot) $.

%These results are strongest for high entropy sources.  The results get weaker as we consider sources with lower starting entropy.  If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}, here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}).

\begin{definition}
Let $(W, X)$ be a pair of random variables.  $W$ has 
\emph{relaxed HILL entropy} at least $k$ conditioned on $X$,
denoted $H^{\hill-rlx}_{\epsilon, s_{sec}}(W|X)\geq k$ if there exists a joint distribution $(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, X),(Y,Z))\leq \epsilon$.
\end{definition}

%\lnote{is there any reason we can't work for the more relaxed notion of HILL, where the condition can be changed, too?}

Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  
%Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
%  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.
We will consider secure sketches that retain relaxed HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.

Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches). For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.  In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y, Z$ such that $\Hav(Y | Z)\geq \tilde{m}$ and $(Y, Z)$ is computationally indistinguishable from $(W, \sketch(W))$.  Sample a sketch $s\leftarrow \sketch(W)$. We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).  %So, by indistinguishability, it must also succeed on $Y$. 
 Consider the following experiment: 1) sample $z\leftarrow Z$, 2) draw $y\leftarrow Y|z$ and 3) $y'\leftarrow B_t(y)$. By indistinguishability $\rec (y',z) = y$ with high probability.
 This means we can construct a large set $C$ from the support of $Y|z$.  $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.

To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
\end{definition}
%We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context. \lnote{ do we need this? if distance is exactly $t'$, then the point is different as long as $t'>0$.  So why not just say "exactly $t'$ in the definition?}

@@

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword.

 \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.  See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.  An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.  We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We can now formalize the intuition above.  A sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{sam}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Let $s_{rec}$ denote the size of the circuit that computes $\rec$.  If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).  The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}\geq t(s_{rec} + n\log |Z|)$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+t\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe inverter $\mathcal{I}_t$:
\begin{enumerate}
\item Input $\vA , \vc = \vA X + W - W'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, \vc$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, \vc_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
Denote by $\vA', \vc'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vc_{i_1,..., i_{2n}}$ (respectively) to these rows.  If no such rows exist go to step (2).
\item Compute $X' = \vA'\vc'$.  If $C- AX'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $X'$.
\end{enumerate}
\end{construction}

$\mathcal{I}_t$ is an efficient inverter/recovery procedure when $t$ is small enough.  We need $t$ to be small enough for step (4) to succeed with probability at least $\frac{1}{\poly(n)}$, furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.  The second condition is to ensure that there are few false positives in step (5).  This condition is satisfied for $t = O(\frac{m}{n}\log n)$, since random codes have high distance with probability $1-e^{-\Omega(n)}$.  The exact statement is in \corref{cor:code high distance}.  Furthermore, steps (3-5) are computable in time $O(n^3)$.
This is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.  We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.  $\mathcal{I}_t$ is efficient as long as $t$ is small enough.  The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\mathcal{I}_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq d\log n (m/n-2)$]
\label{lem:i t poly time}
Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.  Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-1)\log n$.  Then $\mathcal{I}_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
\end{lemma}
\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\mathcal{I}_t$ will run in expected time $O(n^3\log n)$.  Our main theorems apply when $t\leq m/n-2$ with slightly better parameters.  We concentrate on the setting $t\leq d\log n(m/n-2)$.  Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\mathcal{I}_t$ is significantly better than exhaustive search over these error patterns.
